We have tailored our method as follows;

\begin{enumerate}
	\item Interviews and analysis: We conducted open-ended interviews with people working in, or close, to FM in various danish companies.
	\item Design and development: We designed a building automation policy DSL based on our analysis of the interviews
	\item Evaluation: We evaluated the DSL in two ways;
	\begin{enumerate}
		\item By asking our interviewees to have a look at our DSL (not sure!) and fill out a questionnaire
		\item By conducting sessions where students had to write different policies, and then analyzing their behavior
	\end{enumerate}
\end{enumerate}

\section{Interviews and analysis}\label{sec:interviews}
Since building control resides with Facility Management we found it pertinent to interview company employees working on or close to that field. We conducted open-ended interviews with these companies and documented their content mostly by handwritten notes or in some rare cases by audio record. The main purpose of the interviews was to document;

\begin{enumerate}
	\item existing governing rules, implicit or explicit.
	\item existing and requested, sensors and actuators.
	\item requests for new governing rules regardless of their practicality or feasibility.
\end{enumerate}

In order to gather enough material to conceptualize a proper DSL, we interviewed people from the following companies; Br\"{u}el \& Kj\ae r, Bygningsstyrelsen, IT-University of Copenhagen, K\o benhavns Tekniske Skole, ST Aerospace - Denmark and UNI-C.

While conducting the interviews, we pointed out that practicality or feasibility should not influence the requests for new governing rules. This proved hard for the interviewees. Some interviews were therefore conducted over several sessions, giving the interviewees time to think creatively. 

We only used natural language (English and Danish) to give examples of existing building policies and facilitate the discovery of new, relevant ones. This was done to avoid the limitations of technology, like the expressiveness of a programming language.

Finally, this project is based on the requirements defined by the professionals working in Facility Management, and used their stated policies as requirements to be implemented as grammar-passed code using the developed DSL.